A free/open-source Kazakh-Tatar machine translation system

### 2013-06-30 paper/paper.tex
still too wide...

%Another example of a far-reading morphological difference between Tatar and Kazakh reflects the presence of a four-way distinction in Kazakh's 2nd person system, where Tatar only has a two-way distinction.  Kazakh has a distinct pronoun for all combinations of [±plural, ±formal] (сен, сендер, сіз, сіздер), whereas Tatar collapse all pronouns except the [-plural, -formal] син into one pronoun (сез).  This does not only affect affect the pronoun system: since all finite verb forms morphologically agree in person and number with their subject and all possessed nouns agree in person and number with their possessor (with pronouns used in both circumstances only for emphasis and clarification, as is typical in pro-drop languages), the Kazakh and Tatar systems of agreement suffixes have the same pattern.
Another example of a far-reaching morphological difference between Tatar and Kazakh is the presence of a 
four-way distinction in Kazakh's 2\super{nd} person system (both pronouns and agreement suffixes), where Tatar only 
has a two-way distinction.  Kazakh has a distinct pronoun for all combinations of [±plural, ±formal], 
whereas Tatar collapses all pronouns except the [-plural, -formal] into one pronoun, as summarised in Table~\ref{tab:2pprons}.
\begin{table}[htbp]
	\centering
%\begin{subtables}
	%\begin{subtable}[l]
	%\subtable[Kazakh 2nd person pronouns]{
	%\begin{subtable}
	\subfloat[Kazakh 2\super{nd} person pronouns]{
		\begin{tabular}{lll}
			\toprule
			 & {\texttt{[-pl]}} & {\texttt{[+pl]}} \\\midrule
			{\texttt{[-frml]}} & сен & сендер \\
			{\texttt{[+frml]}} & сіз & сіздер \\\bottomrule
		\end{tabular}
	%	\caption{Kazakh 2nd person pronouns}
	%\end{subtable}
	%\end{subtable}
	%\begin{subtable}
	%\begin{subtable}
	%}\subtable[Tatar 2nd person pronouns]{
	}
	\subfloat[Tatar 2\super{nd} person pronouns]{
		\begin{tabular}{lll}
			\toprule
			 & {\texttt{[-pl]}} & {\texttt{[+pl]}} \\\midrule
			{\texttt{[-frml]}} & син & сез \\
			{\texttt{[+frml]}} & сез & сез \\\bottomrule
		\end{tabular}%}
	%	\caption{Kazakh 2nd person pronouns}
	%\end{subtable}
	%\end{subtable}
	}
	\caption{2\super{nd} pers.\ pronoun systems of Kazakh and Tatar}
	\label{tab:2pprons}
\end{table}
%\end{subtables}

>>>>

%Another example of a far-reading morphological difference between Tatar and Kazakh reflects the presence of a four-way distinction in Kazakh's 2nd person system, where Tatar only has a two-way distinction.  Kazakh has a distinct pronoun for all combinations of [±plural, ±formal] (сен, сендер, сіз, сіздер), whereas Tatar collapse all pronouns except the [-plural, -formal] син into one pronoun (сез).  This does not only affect affect the pronoun system: since all finite verb forms morphologically agree in person and number with their subject and all possessed nouns agree in person and number with their possessor (with pronouns used in both circumstances only for emphasis and clarification, as is typical in pro-drop languages), the Kazakh and Tatar systems of agreement suffixes have the same pattern.
Another example of a far-reaching morphological difference between Tatar and Kazakh is the presence of a 
four-way distinction in Kazakh's 2\super{nd} person system (both pronouns and agreement suffixes), where Tatar only 
has a two-way distinction.  Kazakh has a distinct pronoun for all combinations of [±plural, ±formal], 
whereas Tatar collapses all pronouns except the [-plural, -formal] into one pronoun, as summarised in Table~\ref{tab:2pprons}.
\begin{table}[htbp]
	\centering
%\begin{subtables}
	%\begin{subtable}[l]
	%\subtable[Kazakh 2nd person pronouns]{
	%\begin{subtable}
	\subfloat[Kazakh 2\super{nd} person pronouns]{
		\begin{tabular}{lll}
			\toprule
			 & {\texttt{[-pl]}} & {\texttt{[+pl]}} \\\midrule
			{\texttt{[-frm]}} & сен & сендер \\
			{\texttt{[+frm]}} & сіз & сіздер \\\bottomrule
		\end{tabular}
	%	\caption{Kazakh 2nd person pronouns}
	%\end{subtable}
	%\end{subtable}
	%\begin{subtable}
	%\begin{subtable}
	%}\subtable[Tatar 2nd person pronouns]{
	}
	\subfloat[Tatar 2\super{nd} person pronouns]{
		\begin{tabular}{lll}
			\toprule
			 & {\texttt{[-pl]}} & {\texttt{[+pl]}} \\\midrule
			{\texttt{[-frm]}} & син & сез \\
			{\texttt{[+frm]}} & сез & сез \\\bottomrule
		\end{tabular}%}
	%	\caption{Kazakh 2nd person pronouns}
	%\end{subtable}
	%\end{subtable}
	}
	\caption{2\super{nd} pers.\ pronoun systems of Kazakh and Tatar}
	\label{tab:2pprons}
\end{table}
%\end{subtables}
